Reagents: expressing and composing fine-grained concurrency

### 2011-10-31 paper/paper.tex
work on bib

@@

parallel CML's implementation of choice

@@

Haskell's STM

@@

Communicating transactions and company, transactional events

@@

elastic transactions and company, Paper on composing lock-free data
structure operations

>>>>

kcas implementations: \cite{Attiya2008,Fraser2007,Luchangco2003}

@@

pure cml~\cite{Reppy1991}

parallel CML's implementation of choice~\cite{Reppy2009}

@@

Haskell's STM~\cite{Harris2005a}

@@

Communicating transactions~\cite{Lesani2011}, 
Transaction synchronizers~\cite{Luchangco2005},
Transaction communicators~\cite{Luchangco2011},
transactional events~\cite{Donnelly2006}

@@

elastic transactions~\cite{Felber2009} and company,

Paper on composing lock-free data structure operations~\cite{Cederman2010}
